### 2020-07-28 cases_and_policies/rmd/counterfactuals.Rmd
update

```{r otherstates, cache=TRUE, fig.cap="Effect of Removing Policies"}
if (!knitr::is_latex_output()) {
  for( st in c("New York", "Florida", "Michigan", "Georgia", "Massachusetts")) {
    f <- cfplots(st, cfnop, data=df)
    grid.arrange(f$figd, f$figdp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
    grid.arrange(f$figl, f$figp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
  }
}
```

```{r nop-state-figures, cache=TRUE, warning=FALSE}
states <- c("Washington","Illinois","Massachusetts")
for(st in states) {
  f <- cfplots(st, cfnop, data=df)

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figd + ylim(c(-1,5)))
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figl)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}
```

@@

```{r otherstates-deaths, cache=TRUE, fig.cap="Effect of Removing Policies"}
if (!knitr::is_latex_output()) {
  for( st in c("New York", "Florida", "Michigan", "Georgia", "Massachusetts")) {
    f <- cfplots(st, cfnop, yvar="deaths", data=df)
    grid.arrange(f$figd, f$figdp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
    grid.arrange(f$figl, f$figp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
  }
}
```

```{r nop-state-figures-deaths, cache=TRUE, warning=FALSE}
states <- c("Washington","Illinois","Massachusetts")
for(st in states) {
  f <- cfplots(st, cfnop, yvar="deaths", data=df)

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figdp)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figd + ylim(c(-1,5)))
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figl)
  dev.off()

  figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
  print(f$figp)
  dev.off()
}
```

>>>>

# ```{r otherstates, cache=TRUE, fig.cap="Effect of Removing Policies"}
# if (!knitr::is_latex_output()) {
#   for( st in c("New York", "Florida", "Michigan", "Georgia", "Massachusetts")) {
#     f <- cfplots(st, cfnop, data=df)
#     grid.arrange(f$figd, f$figdp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
#     grid.arrange(f$figl, f$figp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
#   }
# }
# ```

# ```{r nop-state-figures, cache=TRUE, warning=FALSE}
# states <- c("Washington","Illinois","Massachusetts")
# for(st in states) {
#   f <- cfplots(st, cfnop, data=df)
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figdp)
#   dev.off()
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figd + ylim(c(-1,5)))
#   dev.off()
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figl)
#   dev.off()
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figp)
#   dev.off()
# }
# ```

@@

# ```{r otherstates-deaths, cache=TRUE, fig.cap="Effect of Removing Policies"}
# if (!knitr::is_latex_output()) {
#   for( st in c("New York", "Florida", "Michigan", "Georgia", "Massachusetts")) {
#     f <- cfplots(st, cfnop, yvar="deaths", data=df)
#     grid.arrange(f$figd, f$figdp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
#     grid.arrange(f$figl, f$figp, nrow=2, top =  textGrob(st,gp=gpar(fontsize=20, font=2)))
#   }
# }
```

# ```{r nop-state-figures-deaths, cache=TRUE, warning=FALSE}
# states <- c("Washington","Illinois","Massachusetts")
# for(st in states) {
#   f <- cfplots(st, cfnop, yvar="deaths", data=df)
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dgrowth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figdp)
#   dev.off()
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-growth_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figd + ylim(c(-1,5)))
#   dev.off()
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-cases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figl)
#   dev.off()
# 
#   figdev(sprintf("%s/tex/tables_and_figures/%s-nop-dcases_deaths_v1.pdf",rootdir,st), width=5,height=3.75)
#   print(f$figp)
#   dev.off()
# }
# ```

### 2020-07-28 cases_and_policies/rmd/regressionsWithPlots.Rmd
update

```{r casedieff, eval = TRUE, cache=FALSE, warning=FALSE, results='asis'}
for (use.national in c(TRUE,FALSE)) {
  sb <- ifelse(use.national, 2, 1)
  sy <- ifelse(use.national, 3, 1)
  pib <- lapply(regs$pib[[sb]][1:4], function(x) x$reg)
  pbiy <- regs$pbiy[[sy]]$reg
  piy <- regs$piy[[sy]]$reg

@@

## Deaths (with cases as information)

```{r deathtables, eval = FALSE, cache=FALSE, warning=FALSE, results='asis'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
df$zero <- 0
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
regs <- mainregressions(sdf,
                        "dlogdd", pols, bvars, infovars, "zero", xlist, ilist, iv, L=L)
showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy);
savetextables(NULL, regs$pbiy, regs$piy, prefix="deaths-casesinfo")
```

@@

```{r deathtablesd, eval = TRUE, cache=FALSE, warning=FALSE, results='asis'}
df$zero <- 0
infovarsd <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
# infovarsd <- list(c("logdd")
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
regs <- mainregressions(sdf,
                        "dlogdd", pols, bvars, infovarsd, "zero", xlist, ilist, iv, L=L)

showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy);
savetextables(regs$pib[[1]], NULL, NULL, prefix="behavior-deathsinfo")
savetextables(c(regs$pib[[1]][1:4], regs$pib[[2]][1:4]), NULL, NULL, prefix="behavior-deathsinfo-NI")
savetextables(c(regs$pib[[1]][1:4]), NULL, NULL, prefix="behavior-deathsinfo-stateinfo")
savetextables(c(regs$pib[[2]][1:4]), NULL, NULL, prefix="behavior-deathsinfo-nationinfo")
savetextables(NULL, regs$pbiy, regs$piy, prefix="deaths-deathsinfo")
savetextables(NULL, regs$pbiy[c(1,3)], regs$piy[c(1,3)], prefix="deaths-deathsinfo-nosplit")

```{r dieff-deaths, eval = TRUE, cache=FALSE, results='asis', warning=FALSE}
for (use.national in c(TRUE,FALSE)) {
  sb <- ifelse(use.national, 2, 1)
  sy <- ifelse(use.national, 3, 1)
  pib <- lapply(regs$pib[[sb]][1:4], function(x) x$reg)
  pbiy <- regs$pbiy[[sy]]$reg
  piy <- regs$piy[[sy]]$reg

@@

## Robustness Check
```{r regsrobust, cache=FALSE, warning=FALSE, results='asis'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
#c("dlogdc", "logdc"))
#infovars2 <- list(c( "logdc"))
tvars <- "dlogtests"  
# xlist <-list(c("z.mask","vote"), c("z.mask","vote")) 
xlist <-list(c("z.mask"), c("z.mask")) 
#xlist <-list(c("mask_percent","vote"), c("mask_percent","vote")) 
interactions <-list("month", statevars)
ilist <- list(interactions, interactions)
iv <- list("0","0") #,"(testratedc ~ lag(testratedc,14))") 
L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
regs <- mainregressions(sdf,
                        "dlogdc", pols, bvars, infovars, tvars, xlist, ilist, iv, L=L)

showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy);
savetextables(NULL, regs$pbiy, regs$piy, prefix="cases-robust")

df$zero <- 0
infovarsd <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
# infovarsd <- list(c("logdd")
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
regs <- mainregressions(sdf,
                        "dlogdd", pols, bvars, infovarsd, "zero", xlist, ilist, iv, L=L)
showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy);

@@

>>>>

```{r casedieff, eval = FALSE, cache=FALSE, warning=FALSE, results='asis'}
for (use.national in c(TRUE,FALSE)) {
  sb <- ifelse(use.national, 2, 1)
  sy <- ifelse(use.national, 3, 1)
  pib <- lapply(regs$pib[[sb]][1:4], function(x) x$reg)
  pbiy <- regs$pbiy[[sy]]$reg
  piy <- regs$piy[[sy]]$reg

@@

<!-- ## Deaths (with cases as information) -->

<!-- ```{r deathtables, eval = FALSE, cache=FALSE, warning=FALSE, results='asis'} -->
<!-- infovars <- list(c("dlogdc", "logdc"), -->
<!--                  c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #, -->
<!-- df$zero <- 0 -->
<!-- L <- 21 -->
<!-- sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) -->
<!-- regs <- mainregressions(sdf, -->
<!--                         "dlogdd", pols, bvars, infovars, "zero", xlist, ilist, iv, L=L) -->
<!-- showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy); -->
<!-- savetextables(NULL, regs$pbiy, regs$piy, prefix="deaths-casesinfo") -->
<!-- ``` -->

@@

```{r deathtablesd, eval = TRUE, cache=FALSE, warning=FALSE, results='asis'}
df$zero <- 0
infovarsd <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
# infovarsd <- list(c("logdd")
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
#sdf <- subset(df, df$date>=as.Date("2020-02-29")) #+L)
regs <- mainregressions(sdf,
                        "dlogdd", pols, bvars, infovarsd, "zero", xlist, ilist, iv, L=L) 
showhtmltables(regs$pib[[1]], regs$pbiy, regs$piy);
savetextables(regs$pib[[1]], NULL, NULL, prefix="behavior-deathsinfo")
savetextables(c(regs$pib[[1]][1:4], regs$pib[[2]][1:4]), NULL, NULL, prefix="behavior-deathsinfo-NI")
savetextables(c(regs$pib[[1]][1:4]), NULL, NULL, prefix="behavior-deathsinfo-stateinfo")
savetextables(c(regs$pib[[2]][1:4]), NULL, NULL, prefix="behavior-deathsinfo-nationinfo")
savetextables(NULL, regs$pbiy, regs$piy, prefix="deaths-deathsinfo")
savetextables(NULL, regs$pbiy[c(1,3)], regs$piy[c(1,3)], prefix="deaths-deathsinfo-nosplit") 
```

```{r dieff-deaths, eval = FALSE, cache=FALSE, results='asis', warning=FALSE}
for (use.national in c(TRUE,FALSE)) {
  sb <- ifelse(use.national, 2, 1)
  sy <- ifelse(use.national, 3, 1)
  pib <- lapply(regs$pib[[sb]][1:4], function(x) x$reg)
  pbiy <- regs$pbiy[[sy]]$reg
  piy <- regs$piy[[sy]]$reg

@@

## Robustness Check
```{r regsrobust, cache=FALSE, warning=FALSE, results='asis'}
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national")) #,
#c("dlogdc", "logdc"))
#infovars2 <- list(c( "logdc"))
tvars <- "dlogtests"
interactions <-list("month", statevars)
ilist <- list(interactions, interactions)
iv <- list("0","0") #,"(testratedc ~ lag(testratedc,14))")

L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdc"
for (k in 1:length(infovars)) {
  # (1) excluding NY 
   xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(1+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding mask wearing rate and log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
  piy[[(2+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(3+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) (1)-(3)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L) 
   sdf2 <- sdf[which(sdf$state!='New York'),]
   xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
   piy[[(4+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars, xlist[[k]]),
              ilist[[k]], 0, L=L)

}

showhtmltables(NULL, NULL, piy);
# savetextables(NULL, NULL,  piy, prefix="cases-robust")

L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national"))
#xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
for (k in 1:length(infovars)) {
  # (1) excluding NY 
  xlist <-list("","")
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L) 
  sdf2 <- sdf[which(sdf$state!='New York'),]
  piy[[(1+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (2) adding mask wearing rate and log(Trump's vote)
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
  piy[[(2+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (3) lagged behavior variables
  sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
  xlist <-list("","")
  piy[[(3+4*(k-1))]] <- policyreg(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                 xlist[[k]]),
              ilist[[k]], 0, L=L)
  # (4) (1)-(3)
   sdf <- subset(df, df$date>=as.Date("2020-02-22")) #+L)
   # sdf2 <- sdf[which(sdf$state!='New York' & sdf$state!='New Jersey' & sdf$state!='Connecticut' & sdf$state!='Massachusetts'),]
   sdf2 <- sdf[which(sdf$state!='New York'),]
   xlist <-list(c("z.mask","logvote"), c("z.mask","logvote"))
   piy[[(4+4*(k-1))]] <- policyreg(sdf2, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", bvars, L+14),
                sprintf("lag(%s, %d)", infovars[[k]], L),
                xlist[[k]]),
              ilist[[k]], 0, L=L)

}
showhtmltables(NULL, NULL, piy);
# savetextables(NULL, NULL,  piy, prefix="deaths-robust")

@@

## Fixed Effects
```{r regsfe, cache=FALSE, warning=FALSE, results='asis'}

source(paste(rootdir,"cases_and_policies/rmd/debiasedfe.R", sep="/"))

#df$pindex <- (df$pshelter+df$pmovie+df$prestaurant+df$pnonessential)/4
df$pindex <- (df$pshelter+df$prestaurant+df$pnonessential)/3

yvar <- "dlogdc"
infovars <- list(c("dlogdc", "logdc"),
                 c("dlogdc", "logdc","dlogdc.national", "logdc.national"))
tvars <- "dlogtests"  
L <- 14
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list()
for (k in 1:length(infovars)) { 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg$beta[1:(9+2*(k-1))] <- m$bc2[1:(9+2*(k-1))] 
  #m$reg$beta[1:(6+2*(k-1))] <- m$bc[1:(6+2*(k-1))]  
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex") 
  # pols <- c("pmaskbus","pk12","pmovie","pindex") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              c(sprintf("lag(%s, %d)", infovars[[k]], L),
                tvars), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m 
  m$reg$beta[1:(6+2*(k-1))] <- m$bc2[1:(6+2*(k-1))] 
  #m$reg$beta[1:(5+2*(k-1))] <- m$bc[1:(5+2*(k-1))] 
  piy[[(4+4*(k-1))]] <- m 
}

 showhtmltables(NULL, NULL,  piy);
# savetextables(NULL, NULL, piy, prefix="cases-fe")

yvar <- "dlogdd"
infovars <- list(c("dlogdd", "logdd"),
                  c("dlogdd", "logdd","dlogdd.national", "logdd.national")) 
L <- 21
sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
piy <- list() 
for (k in 1:length(infovars)) { 
  sdf <- subset(df, df$date>=as.Date("2020-03-07")) #+L)
  pols <- c("pmaskbus","pk12","pmovie","pshelter","prestaurant","pnonessential") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(1+4*(k-1))]] <- m
  m$reg$beta[1:(8+2*(k-1))] <- m$bc2[1:(8+2*(k-1))] 
  #m$reg$beta[1:(5+2*(k-1))] <- m$bc[1:(5+2*(k-1))] 
  piy[[(2+4*(k-1))]] <- m
  pols <- c("pmaskbus","pk12","pindex") 
  #pols <- c("pmaskbus","pk12","pmovie","pindex") 
  m <-  reg_fe(sdf, yvar, pols, NULL,
              sprintf("lag(%s, %d)", infovars[[k]], L), 0, L, "state + month")
  piy[[(3+4*(k-1))]] <- m 
  m$reg$beta[1:(5+2*(k-1))] <- m$bc2[1:(5+2*(k-1))] 
  #m$reg$beta[1:(4+2*(k-1))] <- m$bc[1:(4+2*(k-1))] 
  piy[[(4+4*(k-1))]] <- m
}

 showhtmltables(NULL, NULL,  piy);
# savetextables(NULL, NULL, piy, prefix="deaths-fe")
```
